Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-03 snTomas.tex
added host mass correction section

>>>>

\subsection{Host Galaxy Mass Correction}
\label{sec:HostGalaxyMassCorrection}

\change{
It is now an accepted practice in cosmological analyses using Type Ia
SN to apply a correction to the luminosity of each SN based on the
stellar mass of its host galaxy. Typically this is described as a
simple bifurcation of the SN population: SNe that appear in more
massive hosts are observed to be $\sim$0.08 mag brighter (after
corrections for light curve shape and color) than SNe in low-mass
hosts \citep{Kelly:2010,Sullivan:2010}.  The dividing line for this
purely empirical ``mass step'' correction is generally set around
$10^{10}$\Msun, although this is somewhat arbitrary \citep[see
e.g.][]{Betoule:2014}.  This happens to be very close to the
SN \tomas\ host galaxy mass, which we have measured to be
$10^{10.135}$ \Msun\ based on Eq. 7 of \citet{Taylor:2011}, using the
{\it BPZ} SED fit to define rest-frame optical magnitudes.
}

\change{
The physical mechanism that drives the mass step is not yet
understood, but may be related to the metallicity or age of the SN
progenitor systems. In either case, it is reasonable to expect that
the significance of this effect decreases with redshift, as metal-rich
passive galaxies become much less common at $z>1$.  Indeed, when the
size of the mass step correction is allowed to vary with redshift,
there is no significant evidence that a non-zero mass step is required
at $z>1$ \citep{Rigault:2013,Shafer:2014,Betoule:2014}.  Given the
absence of a clear physical model and the lack of empirical support
for a high-$z$ mass step, we do not apply any correction to SN \tomas
or the control sample.
}
